Trends of SDR in Thessaloniki 

### 2022-10-05 Article.Rmd
Commit 2022-10-05 20:07

```{r echo=F, include=F, cache=T}
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
# knitr::opts_chunk$set(dev        = "png"    )
knitr::opts_chunk$set(out.width  = "80%"   )
knitr::opts_chunk$set(fig.align  = "center" )
# knitr::opts_chunk$set(fig.pos    = '!h'    )

@@

![this is a caption](images/longtermtrendsALL-2.pdf)

<!-- \tiny -->
```{r echo=F, cap="dfsfdffds fs"}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
pander::pander(pp,
               caption = "Table of trends and stats")
```
<!-- \normalsize -->

@@

```{r trackercomm, echo=F, fig.cap="Διάγραμμα συνδέσεων του tracker, κατάλληλη σειρά σύνδεσης (1-2-3) ή (3-2-1)."}
knitr::include_graphics("images/longtermtrendsALL-1.pdf")
```
νονται στο Σχήμα \@ref(fig:trackercomm).

>>>>

```{r echo=F, include=F, cache=T}
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
# knitr::opts_chunk$set(dev        = "png"    )
knitr::opts_chunk$set(out.width  = "80%"   )
knitr::opts_chunk$set(fig.align  = "center" )
knitr::opts_chunk$set(fig.pos    = '!h'    )

@@

```{r trackercomm, echo=F, fig.cap="tracker"}
knitr::include_graphics("./images/longtermtrendsALL-2.pdf")
```

This is it \@ref(fig:trackercomm).

\FloatBarrier

<!-- \tiny -->
```{r echo=F}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
pander::pander(pp,
               caption = "Table of trends and stats")
```
<!-- \normalsize -->

@@
